Multi-level modeling with Openflexo/\FML

### 2021-09-27 6-modelpresentation.tex
Updates from Overleaf

\begin{figure*}
 \centering
    % \includegraphics[width=1.0 \columnwidth]{Figures/Metamodel.pdf}
    \includegraphics[width=1.0 \textwidth]{Figures/Metamodel.pdf}
     \caption{Process management base metamodel}
    \label{fig:BaseMetamodel}
\end{figure*}

@@

\begin{figure*}
 \centering
     \includegraphics[width=1.0 \textwidth]{Figures/AcmeFullArchitecture.pdf}
     \caption{Acme software development process architecture (not all instances are shown for readability reasons)}
    \label{fig:AcmeFullArchitecture}
\end{figure*}

>>>>

\begin{figure*}
 \centering
    % \includegraphics[width=1.0 \columnwidth]{Figures/Metamodel.pdf}
    \includegraphics[width=1.0 \textwidth]{Figures/Metamodel.pdf}
     \caption{Process management base metamodel (\texttt{Gateway}'s associations with \texttt{TaskType} are represented with attributes)}
    \label{fig:BaseMetamodel}
\end{figure*}

@@

\begin{figure*}
 \centering
     \includegraphics[width=1.0 \textwidth]{Figures/AcmeFullArchitecture.pdf}
     \caption{Acme software development process architecture (not all instances are shown for the sake of readability)}
    \label{fig:AcmeFullArchitecture}
\end{figure*}
